\documentclass[10pt,twoside]{article}

\usepackage{7OSME-style}
\usepackage{xcolor}
\usepackage{todonotes}
\usepackage{wrapfig}
\restylefloat{figure}
\usepackage{afterpage}
\usepackage{cutwin}
\usepackage[calc]{adjustbox}
%\captionsetup[sub][font=small,labelfont=bf,textfont=it,margin=\parindent,labelsep=colon]
%\graphicspath{{figures/column_connector}}

\newlength{\strutheight}
\settoheight{\strutheight}{\strut}
%\setlength{\parskip}{\baselineskip}

\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\textfraction}{0.15}
\renewcommand{\floatpagefraction}{0.7}

\input{title}
\authorlist[Biswas, Demaine, Ku]{Amartya Shankha Biswas, Erik D. Demaine, Jason S. Ku}
% the text in square brackets will be shown in the headers; this should be the author surnames
\affiliations{Amartya Shankha Biswas, Erik D. Demaine, and Jason S. Ku \at
Massachusetts Institute of Technology, 32 Vassar St., Cambridge, MA 02139\\
\email{asbiswas@mit.edu}, \email{edemaine@mit.edu}, and \email{jasonku@mit.edu}
}

\makeatletter
  \let\runtitle\@title
  \let\runauthor\shortauthor
\makeatother

\def\runtitle{Efficient Origami Construction of Orthogonal Terrains}

\fancyhead[RE]{\footnotesize \textsf{\textsc{\runauthor}}}
\fancyhead[LO]{\footnotesize \textsf{\textsc{\runtitle}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% ----          start document            ---- %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

\input{abstract}

\input{introduction}

\input{cross_sections/cross_sections}

\input{orthogonal/orthogonal}

% \section{Conclusion}

This paper provides a universal construction to fold orthogonal terrains that is
optimally efficient over its domain, improving upon previous constructions that
were less efficient but applicable to a more general class of target shapes,
i.e., orthogonal polyhedra. Some natural questions arise. Can one improve the
efficiency of the construction for a more restricted set of terrains? For
example, our lower bound is achieved by a maximum height-difference
checkerboard; perhaps one can improve folding efficiency for terrains that are
more slowly varying. Our construction only covers the terrain from above,
allowing the folding to exist anywhere in the space below the terrain. This
allocation is necessary when points of the terrain have more than $2\pi$
material at a point. What is the minimum area of paper that can exist away from
the target terrain over all possible foldings? 

{\bf Acknowledgements:} We thank Martin Demaine, Herng Yi Cheng, Aviv Ovadya,
and Tomohiro Tachi for helpful discussions about this family of problems
at 5OSME.

% reference section
{\small
\bibliographystyle{osmebibstyle}
\bibliography{extrude}
}

% author affiliations are appended at end of paper
\theaffiliations

\end{document}
